---
title: "PSTAT 5LS Lab 6"
author: "YOUR NAME HERE"
date: "Week of November 11, 2024" 
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats250sbi)
```

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Tutorial

```{r tryIt1, error = T}
# Run this chunk to have R show plot the p-value for the lemur example. Be sure to run the setup chunk above first.
plot_t(3.722, df = 53, 
       shadeValues = c(-3.722, 3.722), 
       direction = "beyond")

```

```{r tryIt2, error = T}
# Make sure to enter the value of the test statistic and the degrees of freedom below before running it to calculate the p-value for the lemur example.
2*pt(q =  , df =  , lower.tail = FALSE)

```

```{r loadPenguins, error = T}
penguins <- read.csv("penguins.csv", stringsAsFactors = TRUE)

```

```{r tryIt3, error = T}
# Be sure to specify the variable that you want to make a histogram of below. Remember that we tell R which variable we want to use in a data set with a dollar sign (e.g., dataset$variable) 
hist( ,
     main = "Histogram of Flipper Length",
     xlab = "Flipper length (mm)",
     col = "#09847A")

```

```{r gentoo_subset, error = T}
gentoo <- subset(penguins, penguins$species == "Gentoo")

```

```{r tryIt4, error = T}
# Like before, be sure to specify the variable that you want to make a histogram of below. Remember that now the data set we want the data set with only the Gentoo penguins.
hist( ,
     main = "Histogram of Flipper Length for Gentoo Penguins",
     xlab = "Flipper length (mm)",
     col = "#09847A")

```

```{r tryIt5, error = T}
# Make sure to specify the hypothesized mean in the `mu` argument and the alternative in the `alternative` argument ("two.sided", "less", "greater")
t.test(gentoo$flipper_length_mm, 
       mu =   , 
       alternative =  )

```

```{r tryIt6, error = T}
# Run this code chunk to have R produce summary statistics for the mean flipper length of Gentoo penguins
summary(gentoo$flipper_length_mm)
sd(gentoo$flipper_length_mm)

```

```{r tryIt7, error = T}
# Enter values for `p`, `df`, and `lower.tail` below and then run this chunk to get the critical value
qt(p =  , df =  , lower.tail =  )

```

```{r tryIt8, error = T}
# Specify the value for `conf.level` and then run this chunk to have R produce a 95% confidence interval for the mean flipper length of Gentoo penguins
t.test(gentoo$flipper_length_mm, conf.level = )

```

# Code Cheat Sheet

## `pt(q, df, lower.tail = TRUE)`

- `q` is the x-axis value you want to find an area related to
- `df` is the degrees of freedom of the $t$ distribution
- `lower.tail` determines whether `pt()` finds the area to the left or right of `q`. If `lower.tail = TRUE` (the default), it shades to the left. If `lower.tail = FALSE`, it shades to the right.
  
## `qt(q, df, lower.tail = TRUE)`

- `p` is the probability or area under the curve you want to find an x-axis value for
- `df` is the degrees of freedom of the $t$ distribution
- `lower.tail` determines whether `pt()` finds the area to the left or right of `q`. If `lower.tail = TRUE` (the default), it shades to the left. If `lower.tail = FALSE`, it shades to the right.
  
## `plot_t()`

- `df` refers to the degrees of freedom of the distribution to plot. You must provide this value.
- `shadeValues` is a vector of up to 2 numbers that define the region you want to shade
- `direction` can be one of `less`, `greater`, `beyond`, or `between`, and controls the direction of shading between `shadeValues`. Must be `less` or `greater` if `shadeValues` has only one element; `beyond` or `between` if two
- `col.shade` controls the color of the shaded region, defaults to `"cornflowerblue"`
- `...` lets you specify other graphical parameters to control the appearance of the normal curve (e.g., `lwd`, `lty`, `col`, etc.)

## `t.test(x, alternative, mu, conf.level)`
- `x` is a vector of data values
- `alternative` specifies the direction of the alternative hypothesis; must be one of "two.sided", "less", or "greater"
- `mu` indicates the true value of the mean (under the null hypothesis); defaults to 0
- `conf.level` is the confidence level to be used in constructing a confidence interval; must be between 0 and 1, defaults to 0.95

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`

- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`

- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`

- the y- (vertical) axis label that must be inside a set of double quotes
